The \dealii{} Library, Version 9.3

### 2021-06-19 9.3/paper.tex
improve candi wording

The requirement to download, compile, and install \dealii{} and its dependencies from
source is a major obstacle to many \dealii{} users.
Compiling all dependencies from source can be difficult on operating systems for which
binary packages aren't available or on compute clusters and other machines
without root privileges for the user to install system dependencies.

The source based installation of \dealii{} and its many dependent libraries
can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and
on OS X (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.

@@

\candi{} downloads, unpacks, compiles, and installs an individual
library (called a ``package'' in \candi{}), a list of libraries, or a complete toolchain.
The toolchain installation is the default behavior and the default configuration
ensures that most of the \dealii{} step tutorials can be used directly.
The package installation mode is also useful to generate docker containers.
In toolchain mode, \candi{} checks for and deals appropriately with
dependencies between libraries.

>>>>

The requirement to download, compile, and install \dealii{} and its dependencies from
source is a major obstacle to many \dealii{} users.
Compiling all dependencies from source can be difficult but is a necessity on operating systems for which
binary packages aren't available or on compute clusters and other machines
without root privileges for the user to install system dependencies.

The source based installation of \dealii{} and its many dependent libraries
can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL), and
on OS X (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.

@@

\candi{} downloads, unpacks, compiles, and installs an individual
library (called a ``package'' in \candi{}), a list of libraries, or a complete toolchain.
The toolchain installation is the default behavior and the default configuration
ensures that most of the \dealii{} step tutorials can be used directly.
The package installation mode is also useful to generate docker containers.
In toolchain mode, \candi{} checks for and deals with
dependencies between libraries appropriately.
